The Changing Face of Pediatric Pulmonary Exacerbations in CF (NACFC 2023)

### 2024-01-02 Scott Sagel/PEx in CF/nacfc_2023.qmd
analysis for Yaron started

```{r}
#| include: false
library(tidyverse)
library(gtsummary)
library(ggpubr)
source("~/GitHub/CF/Scott Sagel/PEx in CF/create_pex_analysis_dataset.R")
load("~/Library/CloudStorage/Dropbox/Work/Vigers/CF/Scott Sagel/PEx in CF/Data_Cleaned/analysis_dataset.RData")
# Colors for plots
yellow <- "#f8b80a"
red <- "#e30022"
purple <- "#7b2670"
blue <- "#022451"
```

>>>>

```{r}
#| include: false
library(tidyverse)
library(gtsummary)
library(ggpubr)
source("~/GitHub/CF/Scott Sagel/PEx in CF/create_pex_analysis_dataset.R")
load("~/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Scott Sagel/PEx in CF/Data_Cleaned/analysis_dataset.RData")
# Colors for plots
yellow <- "#f8b80a"
red <- "#e30022"
purple <- "#7b2670"
blue <- "#022451"
```
